Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-25 paper-v1.tex
clean up

\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
\newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.

AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library \cite{OZ}, through the creation of the Issuer and Peer-Reviewer Roles.
\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts. In this way, only the Issuer can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.When the AntReview is accepted by the Issuer, the bounty is paid among Peer-Reviewers.On top of that, the Issuer can cancel the AntReview at any time and withdraw the amount of Ether staked.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta \cite{TimeStamp-Haber}. Pioneers of the blockchain, cited by the Bitcoin whitepaper\cite{Bitcoin}, they were on a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application. In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
\newline Ants-Review is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash. In order to verify if a specific hash is included into a Merkle Tree by leveraging on \emph{MerkleProof.sol} (OpenZeppelin Library), we need to provide a proof, generated from the leaf of interest, that represents the ramification derived from the leaf, the root hash and, finally, the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity.

>>>>

\newline Bob (peer-reviewer) after downloading the file with Alice's paper and requirements, leveraging on the content-addressing feature of IPFS that allows anyone to find the document using an IPFS explorer, can submit a peer-review, before the deadline, by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, specifying the AntReview Identifier as well as the IPFS Hash of the peer-review uploaded on IPFS.
\newline Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, specifying the AntReview Identifier as well as the peer-review identifier, that will transfer the reward specified for the AntReview from the contract to Bob.
\newline If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, specifying the AntReview Identifier, and the contract will transfer the reward for the AntReview back to Alice.

AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library \cite{OZ}, through the creation of the Issuer and Peer-Reviewer Roles.
\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, like an attack to the smart contracts. In this way, only the Issuer can create a new AntReview.
\newline One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber \& W. Scott Stornetta \cite{TimeStamp-Haber}. Pioneers of the blockchain, cited by the Bitcoin whitepaper\cite{Bitcoin}, they were on a mission to solve the problem of immutability of digital records that became reality with the Blockchain and Bitcoin as its first application. In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.
\newline Ants-Review is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree \cite{BayerHaber1992} to achieve immutability and efficiency in verifying the data with a complexity of O(logn) for searching through the tree.
\newline A Merkle tree is a particular type of binary tree, formed by a set of nodes with a large set of leaf nodes at the bottom of the tree representing the hash of the original data, a set of intermediate nodes where each node is the sum of the two children hashes, ending with a single root hash. In order to verify if a specific hash is included into a Merkle Tree by leveraging on \emph{MerkleProof.sol} (OpenZeppelin Library), we need to provide a proof, generated from the leaf of interest, that represents the ramification derived from the leaf, the root hash and, finally, the leaf we want to verify.
\newline The paper and peer-review documents will be included into a Merkle Tree by hashing the data using keccak256, a cryptographic hashing algorithm available in Solidity.
